---
output:
  md_document:
      variant: gfm
html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ggessentials: My ggplot2 essential configurations used for paper figures.

### Functions

 - `geUseTheme`: use a preset theme for plotting (support `bw` or `classic` at the moment)
 - `geGetColors`: get a vector of colors
 - `italicize.string`: italicize strings in a sentence
 - `italicize.plot`: italicize strings in a ggplot

Known issues with `italicize.plot`:

 - overwrites bold font face
 
### Aesthetics

 - `scale_color_ge`/`scale_fill_ge`: selected color scheme

### Themes

 - `theme_bw_ge`
 - `theme_classic_ge`
 
### Installation
```{r install, eval=FALSE}
devtools::install_github("lch14forever/ggessentials")
```

### Usage
```{r usage, message=FALSE, warning=FALSE}
library(ggessentials)

## to get a list of colors (1-17)
colors <- geGetColors(3)

data("iris")
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + 
    geom_point() +
    scale_color_manual(values=colors) +
    theme_bw_ge()
```

#### Italicize a taxon name in a plot

```{r italicize.plot, message=FALSE, warning=FALSE}
p <- ggplot(iris, aes(x=Species, y=Sepal.Width, color=Species)) + 
    geom_boxplot() +
    scale_color_manual(values=colors) +
    theme_bw_ge()

grid::grid.draw(italicize.plot(p, string = c('setosa', 'versicolor')))
```


#### Set theme for the current session

```{r}
## preset the theme
geUseTheme('classic')
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + 
    geom_point() +
    scale_color_manual(values=colors)
```

#### Disrete color scale with `scale_color_ge` or `scale_fill_ge`

```{r scale_color_ge, message=FALSE, warning=FALSE}
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + 
    geom_point() +
    scale_color_ge()
```

```{r scale_fill_ge, message=FALSE, warning=FALSE}
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, fill=Species)) + 
    geom_point(shape=21) +
    scale_fill_ge()
```

